Document Expansion with External Collections for Information Retrieval

### 2016-08-23 paper.tex
added single expansion collection table

%\newcommand\rankeq{\stackrel{\mathclap{\normalfont\mbox{rank}}}{=}}
\newcommand\rankeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily rank}}}{=}}}

@@

\author{[Blind]}
%\author{
%Garrick Sherman and Miles Efron \\
%     \affaddr{Graduate School of Library and Information Science}\\
%       \affaddr{University of Illinois at Urbana-Champaign}\\
%       \email{\{gsherma2, mefron\}@illinois.edu}
%}

@@

% A category with the (minimum) three required fields
%\category{H.3.3}{Information Search and Retrieval}{}

%\terms{}
%\keywords{Entity linking}

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
& {\bf Run} & {\bf $\lambda$} & {\bf MAP} \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & -- & 0.2346 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2 & 0.2273 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.2707 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & -- & 0.2183 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2 & 0.2349 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.2406 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{wt10g} & {\it baseline-ql} & -- & 0.1687 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.7, 0.8 & 0.1735 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.1820 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{blogs06} & {\it baseline-ql} & -- & 0.3064 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.7 & 0.3103 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.2974 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{clueweb09} & {\it baseline-ql} & -- & 0.1117 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2 & 0.1163 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.1176 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. $\uparrow$ indicates statistically significant improvements over baselines \textbf{but I haven't done significance testing yet}.}
\label{table.performance}
\end{table}

%\begin{figure}[!htb]
%\centering
%\includegraphics[width=.85\columnwidth]{figures/sweep-stanbol.pdf}
%\caption{Sweeps over values of $\lambda$ for AP and robust \textit{stanbol} runs.}
%\label{figure.sweeps-stanbol}
%\end{figure}

@@

%Figure \ref{figure.sweeps-stanbol} does not present sweeps over $n$ because variations in performance at different values are negligible for \textit{stanbol} runs. This is due to the low number of entities linked by Stanbol: an average of only 5.96 and 4.70 per document for AP and robust respectively. Notably, our model does not perform well with Stanbol annotations, as seen in Figure \ref{figure.sweeps-stanbol}. Both collections show very slight improvement at $\lambda = 0.1$, but this is not statistically significant and performance declines relative to the baseline at all other values of $\lambda$. We attribute this shortcoming to the overfitting of the Stanbol annotations to specific entity mentions in the text, rather than to concepts relevant to the document.

>>>>

\newcommand\rankeq{\mathrel{\overset{\makebox[0pt]{\mbox{\normalfont\tiny\sffamily rank}}}{=}}}

@@

\author{Garrick Sherman}

@@

@@

\begin{table}[htbp]
\centering
\begin{tabular}{|c|l|c|c|} \hline
{\bf Collection} & {\bf Run} & {\bf $\lambda$} & {\bf MAP} \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{AP} & {\it baseline-ql} & -- & 0.2346 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2 & 0.2273 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.2707 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{Robust} & {\it baseline-ql} & -- & 0.2183 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2 & 0.2349 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.2406 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{wt10g} & {\it baseline-ql} & -- & 0.1687 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.7, 0.8 & 0.1735 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.1820 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{blogs06} & {\it baseline-ql} & -- & 0.3064 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.7 & 0.3103 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.2974 \\ \hline\hline
\rule{0pt}{2.5ex} \multirow{3}{*}{clueweb09} & {\it baseline-ql} & -- & 0.1117 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it baseline-rm} & 0.2 & 0.1163 \\ \cline{2-4}
\rule{0pt}{2.5ex} & {\it exp-ql} & -- & 0.1176 \\ \hline
\end{tabular}
\caption{The top-scoring runs and baselines by MAP. $\uparrow$ indicates statistically significant improvements over baselines \textbf{but I haven't done significance testing yet}.}
\label{table.performance}
\end{table}

@@

\subsection{Is Expansion Worthwhile?}\label{section.results.expansion}

\begin{table}[htbp]
\centering
\begin{tabular}{|l|c|c|c|c|} \hline
& \multicolumn{2}{c}{Self} & \multicolumn{2}{|c|}{Wikipedia} \\ \hline
{\bf Collection} & {\bf $\lambda$} & {\bf MAP} & {\bf $\lambda$} & {\bf MAP} \\ \hline
AP & ? & ? & 0.2 & 0.2662 \\ \hline
Robust & ? & ? & 0.2 & 0.2354 \\ \hline
wt10g & ? & ? & ? & ? \\ \hline
blogs06 & ? & ? & ? & ? \\ \hline
clueweb09 & ? & ? & ? & ? \\ \hline
\end{tabular}
\caption{The top-scoring runs by MAP using only one collection of expansion documents. ``Self'' indicates expansion using the document's original collection while ``Wikipedia'' indicates expansion using Wikipedia.}
\label{table.performance.single}
\end{table}
